Assessing glymphatic transport velocities by adjoint methods

### 2018-10-09 tex/paper.tex
update update

\begin{figure}
\includegraphics[width=0.95\textwidth]{Zoom-PatID-68.png} 
\label{fig2} 
\caption{Shows the percentage intensity increase from baseline at different observation times in the slice (marked red in the left panel) used in the subsequent analysis.}
\end{figure}
Figure ~\ref{fig1} shows the distribution of tracers during 24 hours, see also~\cite{ringstad2017glymphatic} for further information on the imaging procedure.   
Our data (not all shown) consist of a total of 10 MRI observations, including a baseline MRI taken before tracer was injected. The observation points are distributed with 5 observations within 1-2 hours after injection, 1 observation in the timeframes 2-4 hours, 6-9 hours, 24 hours and 48 hours. 
Figure ~\ref{fig2} shows the slice selected for our computations. 
The software Freesurfer was used to segment and align each of the observations, which made it possible to estimate voxelwise intensity increase.

@@

The difference in $S_0$ between observation times were adjusted for in \citep{eidevalnes}.  

@@

\begin{figure}
\centering
\includegraphics[scale=0.2]{27-12-hours-scale-0-1-3.png}  
\caption{The upper row shows the manufactured observation, A ) Shows the manufactured observation at time-point 24 with no noise added. B) Shows the manufactured observation at time-point 24 with an noise amplitude of 0.15 {\color{red} explain noise amplitude}. C)Shows the manufactures observation at time-point 24 with noise amplitude of 0.3. The lower row shows the results with optimized parameter obtained with $alpha=0.0001$, $\beta=1.0$ and $k=27$. D) Shows the  . E)  Shows the  F)  Shows the  }
\end{figure}

\begin{figure}
\centering
\includegraphics[scale=0.2]{27-24-hours-scale-0-1.png}
\caption{The upper row shows the manufactured observation, A ) Shows the manufactured observation at time-point 24 with no noise added. B) Shows the manufactured observation at time-point 24 with a noise amplitude of 0.15 {\color{red} explain noise ampliutde}. C)Shows the manufactures observation at time-point 24 with noise amplitude of 0.3. The lower row shows the results with optimized parameter obtained with $alpha=0.0001$, $\beta=1.0$ and $k=27$. D) Shows the  . E)  Shows the  F)  Shows the  }
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=0.95\textwidth]{Zoom-PatID-68.png} 
\label{fig2} 
\caption{Shows the percentage intensity increase from baseline at different observation times in the slice (marked red in the left panel) used in the subsequent analysis.}
\end{figure}
Figure ~\ref{fig1} shows the distribution of tracers during 24 hours, see also~\cite{ringstad2018brain} for further information on the imaging procedure.   
Our data (not all shown) consist of a total of 10 MRI observations, including a baseline MRI taken before tracer was injected. The observation points are distributed with 5 observations within 1-2 hours after injection, 1 observation in the timeframes 2-4 hours, 6-9 hours, 24 hours and 48 hours. 
Figure ~\ref{fig2} shows the slice selected for our computations. 
The software Freesurfer was used to segment and align each of the observations, which made it possible to estimate voxelwise intensity increase.

@@

The difference in $S_0$ between observation times were adjusted for in \citep{ringstad2018brain}.  

@@

\begin{figure}
\centering
\includegraphics[scale=0.4]{27-12-hours-scale-0-1-3.png}  
\caption{The upper row shows the manufactured observation, A ) Shows the manufactured observation at time-point 24 with no noise added. B) Shows the manufactured observation at time-point 24 with an noise amplitude of 0.15 {\color{red} explain noise amplitude}. C)Shows the manufactures observation at time-point 24 with noise amplitude of 0.3. The lower row shows the results with optimized parameter obtained with $alpha=0.0001$, $\beta=1.0$ and $k=27$. D) Shows the  . E)  Shows the  F)  Shows the  }
\end{figure}

\begin{figure}
\centering
\includegraphics[scale=0.4]{27-24-hours-scale-0-1.png}
\caption{The upper row shows the manufactured observation, A ) Shows the manufactured observation at time-point 24 with no noise added. B) Shows the manufactured observation at time-point 24 with a noise amplitude of 0.15 {\color{red} explain noise ampliutde}. C)Shows the manufactures observation at time-point 24 with noise amplitude of 0.3. The lower row shows the results with optimized parameter obtained with $alpha=0.0001$, $\beta=1.0$ and $k=27$. D) Shows the  . E)  Shows the  F)  Shows the  }
\end{figure}
